---
title: "p8105_hw1_yc4959"
author: "Yimeng Cao"
date: "2026-09-20"
output: github_document
---
This is an R markdown document for 8105 homework 1.

```{r setup, include=FALSE}
library(tidyverse)
```

## Probelm 1

Load the penguins dataset
```{r load data}
data("penguins", package = "palmerpenguins")
```

The penguins dataset contains some penguin information. Important variables include species, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex and year. The size of dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

Create scatter plot of flipper length vs bill length.
```{r scatterplot}
penguins %>%
  ggplot(aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()
```
Save the plot
```{r save plot}
ggsave("penguin_plot.png")
```

## Problem 2

Create a data frame call data_frame：
a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”

```{r Create a data frame}
data_frame = tibble(
  norm_samp = rnorm(10),
  vec_logical = norm_samp > 0,
  vec_character = c("y", "i", "m", "e", "n", "g", "1", "c", "a", "o"),
  vec_factor = factor(c("small", "small", "medium", "medium", "medium", "medium", "medium", "large", "large", "large"))
)
```

Try to take the mean of each variable in your data frame.

```{r Try mean}
mean(pull(data_frame, norm_samp))
mean(pull(data_frame, vec_logical))
mean(pull(data_frame, vec_character))
mean(pull(data_frame, vec_factor))
```
The numeric variable and logical vector can have means, but the 
character and factor vectors cannot have means because they represent 
text and categories.
